On the Synchronization Power of the Openflow Data Plane

### 2015-05-21 inband-sync.tex
i added controller atomicity and order preservation, see that it make sense...

By installing Openflow \emph{flow monitors} with the \textsf{OFPFMF\_INITIAL} optional flag,  
a controller can read the current configuration. 
% %(and subscribe for updates). 
%
%can i match multiple flows in multiple tables? yes, but only for FlowMod, not GroupMod: but that is good enough!%
\liron{I changed a bit the description of flow monitors following Petr's comment, I hope it's more clear now.}
\petr{Not very clear what reading the configuration means: is it done
  in an atomic way?}

@@

When properly configured,
a bundle can be processed in a \emph{packet-atomic} way, in the sense that
each packet is processed according
to the switch configuration either \emph{before} or \emph{after} the
bundle (i.e., all its commands) are executed. 
\liron{we need to disscuss controller atomicity and order preservation inside a bundle}
\petr{Right! :)}

>>>>

In order to read the current configuration of a switch (the existing flow entries), the controller should send
%By installing 
the OpenFlow \emph{add flow monitor} command with the \textsf{OFPFMF\_INITIAL} optional flag.
%In reply the switch will send all the flow entries defined in the switch.
In this paper, we indicate sending this message and gathering the responds (the reply messages containing the flow entries) by \emph{read configuration} statement which also returns the configuration.
%, a controller can read the current configuration. 
% %(and subscribe for updates). 
%
%can i match multiple flows in multiple tables? yes, but only for FlowMod, not GroupMod: but that is good enough!%
\liron{I changed a bit the description of flow monitors following Petr's comment, I hope it's more clear now.}
\petr{Not very clear what reading the configuration means: is it done
  in an atomic way?}

@@

%When properly configured,
Bundle execution is considered controller atomic in the sense that all controllers can observe switch states (configurations) that either \emph{before} or \emph{after} the
bundle (i.e., all its commands) are executed. 
By specifying the flag OFPBF\_ATOMIC,  
a bundle can also be  \emph{packet-atomic}, in a similar sense, which can prevent packets to being processed by intermediate (possibly invalid) configuration during a bundle.
In addition, by specifying the flag OFPBF\_ORDERED,  bundle commands are executed according to the order they were added to the bundle, thereby allowing to perform dependent actions inside a bundle.
\liron{i added controller atomicity and order preservation, see that it make sense...}
